---
output: github_document
params: 
    dp_title: "Data Product"
    config: "empty"
    github_repo_url: "empty"
    board_params_set: "empty"
    creds_set_dried: "empty"
title: "`r params$dp_title`"
---

To build and deploy

### STEP 1: Activate the project

Clone the project, set working directory to project top folder and activate

```{r activate, eval=FALSE}
dpbuild::dp_activate(project_path = ".")
```

### STEP 2: Set environment variables

Set `GITHUB_PAT` as environment variable for `r params$github_repo_url`

```{r set_env, eval=FALSE}
Sys.setenv("GITHUB_PAT" = "<GIHTUB_PAT for the remote url>")
```


Set environment variables as needed to enable evaluation of 

``r glue::glue("{params$creds_set_dried}")``

and order to access the data board 

```{r board, echo=FALSE}
params$board_params_set %>% knitr::kable(.)
```

### STEP 3: Build

This by convention involves sourcing the main script `dp_make.R`

```{r build, eval=FALSE}
source("./dp_make.R")
```


### STEP 4: Deploy

Simple call to `dpdeploy`. By default expects you to be in the project directory

```{r deploy, eval=FALSE}
dpdeploy()
```
